### 2022-09-27 SujetStage/2022-pNetsubjectM2.tex
sujet stage

\begin{description}
\item[\bf Main advisor:] Rabéa Ameur-Boulifa ?
\item[\bf Co-advisors:] Ludovic Henrio and Eric Madelaine?
\item[\bf Place:] Eurecom  -- Sophia Antipolis
\\
or\\
Laboratoire de l'Informatique du Parallélisme (LIP) --
  \'Ecole Normale Supérieure de Lyon
\end{description}

@@

\item  We additionally have defined a notion of refinement between open automata that would benefit from such behavioural types. One additional objective of the internship could be to improve the definition of refinement based on the notion of behavioural types that has been defined in the previous steps.

@@

@@

\bibitem{arxiv-weakbisim}
Rabéa Ameur-Boulifa and Ludovic Henrio and Eric Madelaine:
\newblock {Compositional equivalences based on Open pNets}.
\newblock arXiv {2007.10770} (2020).
 \newblock \url{https://arxiv.org/abs/2007.10770}
\end{thebibliography}

>>>>

\begin{description}
\item[\bf Advisors:] Rabéa Ameur-Boulifa\textsuperscript{(1)} and Ludovic Henrio\textsuperscript{(2)}
\item[\bf Place:] ~\\(1) Eurecom  -- Sophia Antipolis
\\
or\\
(2) Laboratoire de l'Informatique du Parallélisme (LIP) --
  ENS de Lyon

\item[contact:]  \quad \url{rabea.ameur-boulifa@telecom-paris.fr }  \quad \qquad \url{ludovic.henrio@ens-lyon.fr}
\end{description}

@@

\item  We additionally have defined a notion of bisimulation between open automata. One additional objective of the internship could be to prove that behavioural types behave well relatively to bisimilarity.

@@

The internship can be tackled only theoretically on paper, or formalised in an interactive theorem prover, or integrated with existing tools for open automata bisimilarity (based on SMT solvers).

@@

\bibitem{arxiv-weakbisim}
Rabéa Ameur-Boulifa and Ludovic Henrio and Eric Madelaine:
\newblock {Compositional equivalences based on Open pNets}.
\newblock arXiv {2007.10770} (2021).
 \newblock \url{https://arxiv.org/abs/2007.10770}
\end{thebibliography}
